Supporting Information

### 2018-04-08 SupportingInformation.Rmd
typo

![Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_l-\Dsq_u$ reveal the know asymmetry of tail dependence of the Clayton and survival Clayton copulas, and the known symmetry of tail dependence for the normal and Frank copulas. See text for details. $n=35$. \label{fig_stat_testing35}](./Results/stat_results/stat_testing/res_pt35_rankT.pdf)

![Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_l-\Dsq_u$ reveal the know asymmetry of tail dependence of the Clayton and survival Clayton copulas, and the known symmetry of tail dependence for the normal and Frank copulas. See text for details. $n=1000$.\label{fig_stat_testing1000}](./Results/stat_results/stat_testing/res_pt1000_rankT.pdf)

>>>>

![Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the know asymmetry of tail dependence of the Clayton and survival Clayton copulas, and the known symmetry of tail dependence for the normal and Frank copulas. See text for details. $n=35$. \label{fig_stat_testing35}](./Results/stat_results/stat_testing/res_pt35_rankT.pdf)

![Results of tests of whether $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, and $\Dsq_u-\Dsq_l$ reveal the know asymmetry of tail dependence of the Clayton and survival Clayton copulas, and the known symmetry of tail dependence for the normal and Frank copulas. See text for details. $n=1000$.\label{fig_stat_testing1000}](./Results/stat_results/stat_testing/res_pt1000_rankT.pdf)
